Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
Unc example

The vector of parametric coefficient uncertainties $\Delta{p}$ of $\Delta{G}_p(z)$ is defined by:
\begin{equation}
\Delta{p}=\begin{bmatrix}
\hat{b_{0}} - b_{0}\\
\hat{b_{1}} - b_{1}\\
\vdots \\
\hat{b}_{M_G} - b_{M_{G}}\\
\hat{a_{0}} - a_{0}\\
\hat{a_{1}} - a_{1}\\
\vdots\\
\hat{a}_{N_G} - a_{N_{G}}\\
\end{bmatrix}=\begin{bmatrix}
\vec{\hat{b}}\\
\vec{\hat{a}}
\end{bmatrix}-\begin{bmatrix}
\vec{b}\\
\vec{a}
\end{bmatrix}
\end{equation}

@@

Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$,
provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family $\mathfrak{G}(z)$
(Step A), and a transfer function $f$ represented by Eq.~\eqref{FWL_tf} 
(step B) to calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ 
of the controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
model-checker (Step D).

@@

In the first {\sc verify} phase we obtain the following counterexample:
$$
\begin{array}{ll}
\Delta N_G(z) = 0.026506\\
\Delta D_G(z) = 1.000610z+1.002838
\end{array}
$$

@@

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
not going back to the synthesise phase, 
then this illustration doesn't follow the general diagram in Fig.5. 
We need to decide which direction we keep.}
%
$$
\begin{array}{ll}
\Delta N_G(z) {=} 0.026314\\
\Delta D_G(z) {=} 0.999024z{-}1.004785
\end{array}
$$
%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:

@@

@@

\begin{table}[H]
\centering
\begin{tabular}{l | r l}
Benchmark                 & Base    & \\\cline{1-2}
CruiseControl02           & 17\,s   & \\
CruiseControl02$^\dagger$ & 46\,s   & \\
SatelliteB2               & 7\,s    & \\
SatelliteB2$^\dagger$     & 6601\,s & \tbmark\\
SatelliteC2               & 2\,s    & \\
SatelliteC2$^\dagger$     & 76\,s   & \tbmark\\
SpringMassDamper          & 28\,s   & \\
a\_PL1\_SCH2\_IMPL1       & 2704\,s & \\
a\_PL1\_SCH2\_IMPL2       & 538\,s  & \\
a\_PL1\_SCH2\_IMPL3       & 12\,s   & \\
a\_PL1\_SCH3\_IMPL1       & 318\,s  & \\
a\_PL1\_SCH3\_IMPL2       & 967\,s  & \\
a\_PL1\_SCH3\_IMPL3       & 9798\,s & \\
a\_PL1\_SCH4\_IMPL1       & 6304\,s & \\
\end{tabular}

\vspace{0.5em}
\scriptsize{* = solved with interval back-end, $\dagger$ = with uncertainty}
\vspace{0.5em}

\caption{Experimental results. \label{tab:results}}
\end{table}
%---------------------------------

>>>>

The vector of parametric coefficient uncertainties $\Delta{p}$ of $\Delta{G}_p(z)$ is defined by:
\begin{equation}
\Delta{\vec{p}}=\begin{bmatrix}
\hat{b_{0}} - b_{0}\\
\hat{b_{1}} - b_{1}\\
\vdots \\
\hat{b}_{M_G} - b_{M_{G}}\\
\hat{a_{0}} - a_{0}\\
\hat{a_{1}} - a_{1}\\
\vdots\\
\hat{a}_{N_G} - a_{N_{G}}\\
\end{bmatrix}=\begin{bmatrix}
\vec{\hat{b}}\\
\vec{\hat{a}}
\end{bmatrix}-\begin{bmatrix}
\vec{b}\\
\vec{a}
\end{bmatrix}
\end{equation}

@@

Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$,
provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family $\mathfrak{G}(z)$
(Step A), and a transfer function $f$ [eq.  \ref{FWL_tf}] (step B) to
calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
model-checker (Step D).

@@

In the first {\sc verify} phase we obtain the following counterexample:

$$
\blue{
\Delta{\vec{p}} = [0.026506~ 1.000610~ 1.002838]^T
}
$$

%$$
%\begin{array}{ll}
%\Delta N_G(z) = 0.026506\\
%\Delta D_G(z) = 1.000610z+1.002838
%\end{array}
%$$

@@

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
not going back to the synthesise phase, 
then this illustration doesn't follow the general diagram in Fig.5. 
We need to decide which direction we keep.}
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$
\blue{
\Delta{\vec{p}} = [0.026314~ 0.999024~ {-}1.004785]^T
}
$$

%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:

@@

\blue{
This candidate solution is validated as the final solution by the next 
{\sc verify} phase.
}

@@

\begin{figure}[H]
\centering
\begin{tabular}{l | r r l}
Benchmark              & Base     & Unc     & \\\cline{1-4}
CruiseControl02        & 17\,s    & 46\,s   & \\
SatelliteB2            & 7\,s     & 6601\,s & \tbmark\\
SatelliteC2            & 2\,s     & 76\,s   & \tbmark\\
SpringMassDamper       & 28\,s    & \xmark  &
\end{tabular}

\vspace{0.5em}
\scriptsize{* = solved with interval back-end, \xmark = uncontrollable}
\vspace{0.5em}

\caption{Experimental results. \textcolor{red}{It should be a table and not a figure.} \label{tab:results}}
\end{figure}
%---------------------------------
